\part{Introduction to LibML}
\setcounter{chapter}{1}
\section{What is LibML ?}
LibML (pronounced `libmel', like `OCaml') means `Machine Learning Library'.
It is written in OCaml, and is meant to regroup implementations of various
machine learning algorithms.

\section{LibML project's goals}
\begin{itemize}
\item Contribute to the free software communauty, and create a space where
anyone can add a family of learning structures/algorithms. One of the primary
goals is to save time using existing/inherited structures or methods, and to create
a reliable architecture. We think this leads to less bugs and to better code
checking processes.
\item Enable one to simply make programs in which machine learning
is involved.
\item Use a beautiful and reliable language: \textit{OCaml}, and take benefit
from its object oriented implementation. LibML is meant to
be object oriented; its architecture relies on classes inheritance and
interaction between objects.
\end{itemize}

\newpage
\section{About the authors}
\begin{itemize}

\item Olivier RICORDEAU\\
In charge of:
\begin{itemize}
\item library compilation (see \vref{installing:compilation})
\item library packaging (see \vref{installing:packaging})
\item library installation (see \vref{installing:part})
\item documentation generation (see \vref{installing:documentation})
\item enhanced backpropagation implementation (see
\vref{nn:enhancedbackprop})
\item user manual
\item test suite
\end{itemize} 

\item Matthieu LAGACHERIE\\
In charge of:
\begin{itemize}
\item most of the neural networks part (see \vref{algorithms:nn})
\item genetic programming (see \vref{algorithms:gp})
\item web site management \cite{libml:web}.
\item test suite
\item TODO: fill this!
\end{itemize} 

\end{itemize}
 
\newpage
\section{Thanks}
LibML's developers would like to thank the following people:

\begin{itemize}
\item the savannah.org hackers team, because they provide us an online
powerful development and project managemement tool.
\item Richard Stallman, for the GNU project.
\item the people who work on the \textit{OCaml} compiler, and to those who
provide us useful tools.
\item all the people who give their time everyday for the free software
communauty.
\item and last but not least: to our coffee machines. Nothing would be
possible without them.
\end{itemize}

\newpage
\section{LibML's license.}
LibML is distributed under the terms of the \textit{GNU GPL} license
\footnote{See \vref{appendix:gpl} for a full text version of the \textit{GPL}
license.}.
\input{copying}
